Benchmarking on Rigetti architecture

### 2022-06-23 txt/manuscript.tex
new file with the manuscript

%
%\begin{minipage}{0.495\linewidth}
%	\begin{equation*}
%		\begin{split}
%			\text{\textbf{Primal problem:}} \\
%			\text{maximize:}\quad & \tr(X J(\Phi)) \\[2mm]
%			\text{subject to:}\quad &  \left[ \begin{array}{cc}\Id_{d_2} \otimes \rho & X \\ X^* & \Id_{d_2} \otimes \rho  \end{array} \right] \ge 0 \\
%			& \rho \in \HH_d^+\\ 
%			& X \in M_{d1,d2}.
%		\end{split}
%	\end{equation*}
%\end{minipage}
%\begin{minipage}{0.495\linewidth}
%	\begin{equation*}
%		\begin{split}
%			\text{\textbf{Dual problem:}} \\
%			\text{minimize:}\quad & ||\tr_1(Y)||_\infty \\[2mm]
%			\text{subject to:}\quad & \left[ \begin{array}{cc}Y & -J(\Phi) \\ -J(\Phi) &  Y \end{array} \right] \ge 0 \\
%			& Y \in \HH_{d_1d_2}^+.
%		\end{split}
%	\end{equation*}
%	\vspace{0.5cm}
%\end{minipage}

@@

\begin{theorem}\label{rozrpomiarow}
Let us $\mathcal{P}_U, \mathcal{P}_\1$ be two von Neumann measurements,  $U = H_2 \diag(1, e^{i \phi}) H_2^\dagger$, $\phi \in [0, 2\pi)$ such that $0 \not\in W(U)$.  If there exists the discriminator $\rho \in \Omega_2$ of the form $\rho = \frac{1}{2}\rho_1 + \frac{1}{2} \rho_2$ such that
	\begin{enumerate}
		\item $\rho_1,\rho_2 \in \Omega_2$
		\item $\Pi_1 \rho_1 \Pi_1 = \rho_1$,
		\item $\Pi_2 \rho_2 \Pi_2 = \rho_2$,
		\item  $\mathrm{diag}(\rho_1) = \mathrm{diag}(\rho_2)$,
	\end{enumerate}
	where $\Pi_1,\Pi_2 $ are the projectors on the subspaces
	spanned by the eigenvectors corresponding to $\lambda_1$ and $\lambda_2$ of $U$. Then  we have 
	\begin{equation}
	||\mathcal{P}_U - \mathcal{P}_\Id||_\diamond = 2\sqrt{1- \left|\frac{1+e^{i \phi}}{2}\right|^2}.
	\end{equation}
	%gdzie $\lambda_1, \lambda_n$ jest odpowiednio najmniejszą i największą wartością własną $U\in \mathrm{U}(\XX)$.
\end{theorem}
\begin{proof} From \ref{th:minE} we have 
	\begin{equation}
	\begin{split}
	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond =\min_{E \in \diaguni_2} ||\mathcal{P}_{UE} - \mathcal{P}_{\1}||_\diamond = \min_{E \in \diaguni_2}|| \Delta \left(\Phi_{E^\dagger U^\dagger} - \Phi_{\1} \right) ||_\diamond \le \\ \le \min_{E \in \diaguni_2} ||\Delta||_\diamond || \Phi_{E^\dagger U^\dagger} - \Phi_{\1}  ||_\diamond \le \min_{\diaguni_2}|| \Phi_{E^\dagger U^\dagger} - \Phi_{\1} ||_\diamond.
	\end{split}
	\end{equation}
The diamond norm between two unitary channels can be calculated by 
	\begin{equation}
	\min_{E \in \diaguni_2}||\Phi_{E^\dagger U^\dagger} - \Phi_\1||_\diamond  = \min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
	\end{equation}
Hence,  it is enough to calculate the formula
\begin{equation}
\begin{split}
\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
\end{split}
\end{equation}
Recall, let us note $U$ as
\begin{equation}
U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
\end{equation}
where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is of the form $\ket{x_1} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$, whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = \left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$. 
Consider two cases:

@@

	$2^\circ$ Consider  $\phi \not = \pi$. 
The spectrum of $U$ is of the form $\sigma(U) = \{e^{\mathbf{i} \phi},1\}$. Hence $0 \not\in W\left(U\right)$.  Let us note $U$ as 
	\begin{equation}
	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}.
	\end{equation}
Based on Lemma 5 in~\cite{puchala2018strategies} let us take $\rho_1 = \ketbra{x_1}{x_1}$ and $\rho_2 = \ketbra{x_2}{x_2}$. Obviously,  $\rho_1,\rho_2 \in \Omega_2$ and satisfies the requirements of theorem. Hence, the discriminator $\rho \in \Omega_2$ has the form 
	\begin{equation}
	\rho = \frac{1}{2} \rho_1 + \frac{1}{2}\rho_2 = \left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right)
	\end{equation}
%and 
%	\begin{equation}
%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond = 2 \sqrt{1 - \left| \frac{1 + e^{\mathbf{i} \phi}}{2}\right|^2 },
%	\end{equation}

%	
%	$1^\circ$ For $E = \1_\XX$ and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$ we have 
%	\begin{equation}
%	\tr \left(U\rho \right) = \frac{1}{2} \lambda_1 \tr\left(\rho_1 \Pi_1 \right) + \frac{1}{2} \lambda_2 \tr\left(\rho_2\Pi_2 \right) = \frac{\lambda_1+\lambda_2}{2}. 
%	\end{equation}
%	Therefore, we have
%	\begin{equation}
%	2\sqrt{1 -  |\tr(UE \rho )|^2} =  2 \sqrt{1- \left|\frac{\lambda_1+\lambda_2}{2}\right|^2}.
%	\end{equation}
%	$2^\circ$ Let us consider  $E \in \diaguni_2$ given by $E = \sum_{i=1}^2 e_i \ketbra{i}{i}$   and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$. Then we have 
%	\begin{equation}
%	\begin{split}
%	\tr \left(UE\rho \right) &= \frac{1}{2}\lambda_1 \tr \left(\rho_1 \Pi_1 E \right) + \frac{1}{2}\lambda_2 \tr \left(\rho_2 \Pi_2 E \right) = \\& = \frac{1}{2} \lambda_1 \sum_{i =1}^2 \bra{i}\rho_1 \ket{i} e_i + \frac{1}{2} \lambda_2 \sum_{i =1}^2 \bra{i}\rho_2 \ket{i} e_i = \frac{1}{2} \left(\lambda_1 + \lambda_2\right)\sum_{i=1}^2 \bra{i}\rho_1 \ket{i} e_i.
%	\end{split}
%	\end{equation} 
%So we have 
%	\begin{equation}
%	\left|\tr\left(UE \rho \right) \right| = \left|\frac{\lambda_1+\lambda_2}{2} \right| \cdot \left| \sum_{i=1}^2 \bra{i}\rho_2 \ket{i} e_i \right| \le \left|\frac{\lambda_1+\lambda_2}{2} \right|.
%	\end{equation}
%	It implies that
%	\begin{equation}
%	\sqrt{1 - \left|\frac{\lambda_1+\lambda_2}{2}\right|^2} \le \sqrt{1 -  |\tr(UE \rho)|^2} \le\sqrt{1 - \min_{\rho \in\Omega_2} |\tr(UE \rho )|^2}.
%	\end{equation}
%	Hence we obtain
%	\begin{equation}
%	\begin{split}
%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &=  \max_{\rho \in \Omega_2} \sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} \le \\& \le 2 \sqrt{1 -\left|\frac{\lambda_1+\lambda_2}{2} \right|^2}
%	\end{split}
%	\end{equation}
For $\rho =  \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$ we obtain
	\begin{equation}
	\begin{split}
	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &= \sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} = \\& \sum_{i=1}^2  \sqrt{\left(\bra{i}U^\dagger\rho U \ket{i} + \bra{i} \rho \ket{i} \right)^2 - 4|\bra{i}\rho U \ket{i}|^2} = \\& \sum_{i=1}^2  \sqrt{4 \bra{i}\rho \ket{i}^2 - 4 \left| \frac{\lambda_1 \bra{i}\rho_1 \ket{i} + \lambda_2\bra{i} \rho_2\ket{i}}{2}\right|^2} =\\&  \sum_{i=1}^2  \sqrt{4 \bra{i}\rho \ket{i}^2 - 4 \bra{i} \rho \ket{i} \left| \frac{\lambda_1 + \lambda_2}{2}\right|^2} = \\&  \sum_{i=1}^2 2 \bra{i} \rho \ket{i} \sqrt{1 -\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } = \\& 2 \sqrt{1 -\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } = 
	2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } ,
	\end{split}
	\end{equation}
which completes the proof.
\end{proof}

>>>>

%
%\begin{minipage}{0.495\linewidth}
%	\begin{equation*}
%		\begin{split}
%			\text{\textbf{Primal problem:}} \\
%			\text{maximize:}\quad & \tr(X J(\Phi)) \\[2mm]
%			\text{subject to:}\quad &  \left[ \begin{array}{cc}\Id_{d_2} 
%\otimes \rho & X \\ X^* & \Id_{d_2} \otimes \rho  \end{array} \right] \ge 0 \\
%			& \rho \in \HH_d^+\\ 
%			& X \in M_{d1,d2}.
%		\end{split}
%	\end{equation*}
%\end{minipage}
%\begin{minipage}{0.495\linewidth}
%	\begin{equation*}
%		\begin{split}
%			\text{\textbf{Dual problem:}} \\
%			\text{minimize:}\quad & ||\tr_1(Y)||_\infty \\[2mm]
%			\text{subject to:}\quad & \left[ \begin{array}{cc}Y & -J(\Phi) \\ 
%-J(\Phi) &  Y \end{array} \right] \ge 0 \\
%			& Y \in \HH_{d_1d_2}^+.
%		\end{split}
%	\end{equation*}
%	\vspace{0.5cm}
%\end{minipage}

@@

\begin{theorem}\label{rozrpomiarow}
Let us $\mathcal{P}_U, \mathcal{P}_\1$ be two von Neumann measurements,  $U = 
H_2 \diag(1, e^{i \phi}) H_2^\dagger$, $\phi \in [0, 2\pi)$ such that $0 
\not\in W(U)$.  If there exists the discriminator $\rho \in \Omega_2$ of the 
form $\rho = \frac{1}{2}\rho_1 + \frac{1}{2} \rho_2$ such that
	\begin{enumerate}
		\item $\rho_1,\rho_2 \in \Omega_2$
		\item $\Pi_1 \rho_1 \Pi_1 = \rho_1$,
		\item $\Pi_2 \rho_2 \Pi_2 = \rho_2$,
		\item  $\mathrm{diag}(\rho_1) = \mathrm{diag}(\rho_2)$,
	\end{enumerate}
	where $\Pi_1,\Pi_2 $ are the projectors on the subspaces
	spanned by the eigenvectors corresponding to $\lambda_1$ and $\lambda_2$ of 
	$U$. Then  we have 
	\begin{equation}
	||\mathcal{P}_U - \mathcal{P}_\Id||_\diamond = 2\sqrt{1- \left|\frac{1+e^{i 
	\phi}}{2}\right|^2}.
	\end{equation}
	%gdzie $\lambda_1, \lambda_n$ jest odpowiednio najmniejszą i największą 
	%wartością własną $U\in \mathrm{U}(\XX)$.
\end{theorem}
\begin{proof} From \ref{th:minE} we have 
	\begin{equation}
	\begin{split}
	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond =\min_{E \in \diaguni_2} 
	||\mathcal{P}_{UE} - \mathcal{P}_{\1}||_\diamond = \min_{E \in 
	\diaguni_2}|| \Delta \left(\Phi_{E^\dagger U^\dagger} - \Phi_{\1} \right) 
	||_\diamond \le \\ \le \min_{E \in \diaguni_2} ||\Delta||_\diamond || 
	\Phi_{E^\dagger U^\dagger} - \Phi_{\1}  ||_\diamond \le \min_{\diaguni_2}|| 
	\Phi_{E^\dagger U^\dagger} - \Phi_{\1} ||_\diamond.
	\end{split}
	\end{equation}
The diamond norm between two unitary channels can be calculated by 
	\begin{equation}
	\min_{E \in \diaguni_2}||\Phi_{E^\dagger U^\dagger} - \Phi_\1||_\diamond  = 
	\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho 
	)|^2}.
	\end{equation}
Hence,  it is enough to calculate the formula
\begin{equation}
\begin{split}
\min_{E \in \diaguni_2} 2\sqrt{1 - \min_{\rho \in \Omega_2} |\tr(UE \rho )|^2}.
\end{split}
\end{equation}
Recall, let us note $U$ as
\begin{equation}
U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}, 
\end{equation}
where  for eigenvector $\lambda_1 = e^{\mathbf{i} \phi}$ the eigenvector is of 
the form $\ket{x_1} = 
\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\-\frac{1}{\sqrt{2}}\end{array}\right]$,
 whereas for  $\lambda_2 = 1$ we have $\ket{x_2} = 
\left[\begin{array}{c}\frac{1}{\sqrt{2}}\\\frac{1}{\sqrt{2}}\end{array}\right]$.

Consider two cases:

@@

	$2^\circ$ Consider  $\phi \not = \pi$. 
The spectrum of $U$ is of the form $\sigma(U) = \{e^{\mathbf{i} \phi},1\}$. 
Hence $0 \not\in W\left(U\right)$.  Let us note $U$ as 
	\begin{equation}
	U= \lambda_1 \ketbra{x_1}{x_1} + \lambda_2 \ketbra{x_1}{x_2}.
	\end{equation}
Based on Lemma 5 in~\cite{puchala2018strategies} let us take $\rho_1 = 
\ketbra{x_1}{x_1}$ and $\rho_2 = \ketbra{x_2}{x_2}$. Obviously,  $\rho_1,\rho_2 
\in \Omega_2$ and satisfies the requirements of theorem. Hence, the 
discriminator $\rho \in \Omega_2$ has the form 
	\begin{equation}
	\rho = \frac{1}{2} \rho_1 + \frac{1}{2}\rho_2 = 
	\left(\begin{array}{cc}\frac{1}{2}&0\\0&\frac{1}{2}\end{array}\right)
	\end{equation}
%and 
%	\begin{equation}
%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond = 2 \sqrt{1 - \left| \frac{1 
%+ e^{\mathbf{i} \phi}}{2}\right|^2 },
%	\end{equation}

%	
%	$1^\circ$ For $E = \1_\XX$ and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} 
%\rho_2$ we have 
%	\begin{equation}
%	\tr \left(U\rho \right) = \frac{1}{2} \lambda_1 \tr\left(\rho_1 \Pi_1 
%\right) + \frac{1}{2} \lambda_2 \tr\left(\rho_2\Pi_2 \right) = 
%\frac{\lambda_1+\lambda_2}{2}. 
%	\end{equation}
%	Therefore, we have
%	\begin{equation}
%	2\sqrt{1 -  |\tr(UE \rho )|^2} =  2 \sqrt{1- 
%\left|\frac{\lambda_1+\lambda_2}{2}\right|^2}.
%	\end{equation}
%	$2^\circ$ Let us consider  $E \in \diaguni_2$ given by $E = \sum_{i=1}^2 
%e_i \ketbra{i}{i}$   and $\rho  = \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$. 
%Then we have 
%	\begin{equation}
%	\begin{split}
%	\tr \left(UE\rho \right) &= \frac{1}{2}\lambda_1 \tr \left(\rho_1 \Pi_1 E 
%\right) + \frac{1}{2}\lambda_2 \tr \left(\rho_2 \Pi_2 E \right) = \\& = 
%\frac{1}{2} \lambda_1 \sum_{i =1}^2 \bra{i}\rho_1 \ket{i} e_i + \frac{1}{2} 
%\lambda_2 \sum_{i =1}^2 \bra{i}\rho_2 \ket{i} e_i = \frac{1}{2} 
%\left(\lambda_1 
%+ \lambda_2\right)\sum_{i=1}^2 \bra{i}\rho_1 \ket{i} e_i.
%	\end{split}
%	\end{equation} 
%So we have 
%	\begin{equation}
%	\left|\tr\left(UE \rho \right) \right| = 
%\left|\frac{\lambda_1+\lambda_2}{2} \right| \cdot \left| \sum_{i=1}^2 
%\bra{i}\rho_2 \ket{i} e_i \right| \le \left|\frac{\lambda_1+\lambda_2}{2} 
%\right|.
%	\end{equation}
%	It implies that
%	\begin{equation}
%	\sqrt{1 - \left|\frac{\lambda_1+\lambda_2}{2}\right|^2} \le \sqrt{1 -  
%|\tr(UE \rho)|^2} \le\sqrt{1 - \min_{\rho \in\Omega_2} |\tr(UE \rho )|^2}.
%	\end{equation}
%	Hence we obtain
%	\begin{equation}
%	\begin{split}
%	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &=  \max_{\rho \in \Omega_2} 
%\sum_{i=1}^2  \sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} 
%\right)^2 - 4|\bra{i}\rho\ket{u_i}|^2} \le \\& \le 2 \sqrt{1 
%-\left|\frac{\lambda_1+\lambda_2}{2} \right|^2}
%	\end{split}
%	\end{equation}
For $\rho =  \frac{1}{2} \rho_1 + \frac{1}{2} \rho_2$ we obtain
	\begin{equation}
	\begin{split}
	||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond &= \sum_{i=1}^2  
	\sqrt{\left(\bra{u_i}\rho\ket{u_i} + \bra{i} \rho \ket{i} \right)^2 - 
	4|\bra{i}\rho\ket{u_i}|^2} = \\& \sum_{i=1}^2  
	\sqrt{\left(\bra{i}U^\dagger\rho U \ket{i} + \bra{i} \rho \ket{i} \right)^2 
	- 4|\bra{i}\rho U \ket{i}|^2} = \\& \sum_{i=1}^2  \sqrt{4 \bra{i}\rho 
	\ket{i}^2 - 4 \left| \frac{\lambda_1 \bra{i}\rho_1 \ket{i} + 
	\lambda_2\bra{i} \rho_2\ket{i}}{2}\right|^2} =\\&  \sum_{i=1}^2  \sqrt{4 
	\bra{i}\rho \ket{i}^2 - 4 \bra{i} \rho \ket{i} \left| \frac{\lambda_1 + 
	\lambda_2}{2}\right|^2} = \\&  \sum_{i=1}^2 2 \bra{i} \rho \ket{i} \sqrt{1 
	-\left| \frac{\lambda_1 + \lambda_2}{2}\right|^2 } = \\& 2 \sqrt{1 -\left| 
	\frac{\lambda_1 + \lambda_2}{2}\right|^2 } = 
	2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } ,
	\end{split}
	\end{equation}
which completes the proof.
\end{proof}
